### 2024-05-18 fantasy-football.qmd
20240518 - update to save only to html and revealjs
20240518 - video introduction to American football
20240518 - video titles

@@

::: {.content-visible when-format="html"}

![Video that provides introduction to fantasy football](images/fantasyFootball.mp4){width=100%}

>>>>

::: {.content-visible when-format="html:js"}

![Video that provides introduction to American football.](images/football.mp4){width=100%}

@@

::: {.content-visible when-format="html:js"}

![Video that provides introduction to fantasy football.](images/fantasyFootball.mp4){width=100%}
